Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-14 relatedwork.tex
More text added to related work section.

% vidya: this probably should be its own section
% hawkfish: Not sure it is big enough, but I can see the logic.

@@

There are several bodies of research on developing semantic parsers and grammars for interpreting time and date expressions. Lee \textit{et al} use a combinatory categorical grammar by combining the TIMEX3 standard~\cite{timex3} with contextual cues such as document creation time to determine the reference for parsing time expressions such as `2nd Friday of July'~\cite{LeeADZ14}.

>>>>

@@

There are several bodies of research on developing semantic parsers and grammars for interpreting time and date expressions. Lee \textit{et al} use a combinatory categorical grammar by combining the TIMEX3 standard~\cite{timex3} with contextual cues such as document creation time to determine the reference for parsing time expressions such as `2nd Friday of July'~\cite{LeeADZ14}. Related work by Gabor \textit{et al.} employs a probabilistic approach for learning to interpret temporal phrases~\cite{Angeli:2012}. Han and Lavie developed a formalism called the Time Calculus for Natural Language (TCNL), designed to capture the meaning of temporal expressions in natural language. In this formalism, each temporal expression is converted to a formula in TCNL, which then can be processed to calculate the value of a temporal expression. Their temporal focus tracking mechanism allows correct interpretation of cases like `I am free next week. How
about Friday?', where the TCNL formula for Friday, reflects the occurrence of `next' in the preceding sentence~\cite{Han:2004}.  In all this previous research using natural language techniques, the interpretation of temporal expressions are done individually, using the presence of lexical tokens such as `next' and `past' along with the tense of the verb tokens.

Ou work differs from these previous methods for parsing date-time expressions as we are using an entire column of data as context without the necessary presence of rich lexical identifiers to determine temporal context. This sort of data tends to be prevalent in datasets that are used in visualizations.
